### 2014-06-03 writing/S'14 paper/join.tex
Revised recursion section
Tweaks

\section{Relation composition}

If a model is to learn the behavior of a relational logic like the one
presented here from a finite amount data, it must be able to learn to
deduce new relations from seen relations in a sound and complete
manner. The simplest such deductions involve atomic statements using
the relations in Table~\ref{b-table}. For instance, given that $a
\natrev b$ and $b \natrev c$, one can conclude that $a \natrev c$, by
basic set-theoretic reasoning (transitivity of $\natrev$). Similarly,
from $a \natfor b$ and $b \natneg c$, it follows that $a \natalt c$.
The full set of sound inferences of this form is summarized in
Table~\ref{tab:jointable}.

@@

\begin{figure}[htp]
  \centering
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \newcommand{\labelednode}[4]{\put(#1,#2){\oval(1.5,1)}\put(#1,#2){\makebox(0,0){$\begin{array}{c}#3\\\{#4\}\end{array}$}}}
    \setlength{\unitlength}{1cm}
    \begin{picture}(5,5.5)
      \labelednode{2.50}{5}{a}{1,2,3}

@@

      \labelednode{0.75}{3.5}{b}{1,2}
      \labelednode{2.50}{3.5}{c}{1,3}
      \labelednode{4.25}{3.5}{d}{2,3}

@@

      \labelednode{0.75}{2}{e}{1}
      \labelednode{2.50}{2}{f}{2}
      \labelednode{4.25}{2}{g}{3}

@@

      \labelednode{2.5}{0.5}{h}{}
    \end{picture}
    \caption{Simple boolean model.}
  \end{subfigure}
  \qquad
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \setlength{\tabcolsep}{12pt}
    \begin{tabular}[b]{c  c}
      \toprule
      Train & Test \\
      \midrule
                    & $b \nateq b$ \\
      $b \natcov c$ &               \\
                    & $b \natcov d$ \\
                    & $b \natrev e$ \\
      $c \natcov d$ &               \\
      $c \natrev e$ &               \\
                    & \strikeout{$c \natneg f$} \\
      $c \natrev g$ &               \\ 
                    & $e \natfor b$ \\
      $e \natfor c$ &               \\[-1ex]
      $\vdots$      & $\vdots$ \\
      \bottomrule
    \end{tabular}

>>>>

\section{Relation composition}\label{sec:join}

If a model is to learn the behavior of a relational logic like the one
presented here from a finite amount data, it must be able to learn to
deduce new relations from seen relations in a sound and complete
manner. The simplest such deductions involve atomic statements using
the relations in Table~\ref{b-table}. For instance, given that $a
\natrev b$ and $b \natrev c$, one can conclude that $a \natrev c$, by
basic set-theoretic reasoning (transitivity of $\natrev$). Similarly,
from $a \natfor b$ and $b \natneg c$, it follows that $a \natalt c$.
The full set of sound inferences of this form is summarized in
Table~\ref{tab:jointable}; blank cells correspond to pairs of relations
for which no valid inference can be drawn in our logic.

@@

\begin{figure}[htp]
  \centering
  \begin{subfigure}[t]{0.4\textwidth}
    \centering
    \newcommand{\labelednode}[4]{\put(#1,#2){\oval(1.5,1)}\put(#1,#2){\makebox(0,0){$\begin{array}{c}#3\\\{#4\}\end{array}$}}}
    \setlength{\unitlength}{1cm}
    \begin{picture}(5,5.5)
      \labelednode{2.50}{5}{}{1,2,3}

@@

      \labelednode{0.75}{3.5}{a,b}{1,2}
      \labelednode{2.50}{3.5}{c}{1,3}
      \labelednode{4.25}{3.5}{d}{2,3}

@@

      \labelednode{0.75}{2}{e,f}{1}
      \labelednode{2.50}{2}{}{2}
      \labelednode{4.25}{2}{g,h}{3}

@@

      \labelednode{2.5}{0.5}{}{}
    \end{picture}
    \caption{Simple boolean model. The letters name the sets. Not all sets have names, and
    some sets have multiple names, so that learning $\nateq$ is non-trivial.}
  \end{subfigure}
  \qquad
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \setlength{\tabcolsep}{12pt}
    \begin{tabular}[b]{c  c}
      \toprule
      Train & Test \\
      \midrule
                    & $b \nateq b$ \\
      $b \natcov c$ &               \\
                    & $b \natcov d$ \\
                    & \strikeout{$b \natrev e$} \\
      $c \natcov d$ &               \\
      $c \natrev e$ &               \\
                    & \strikeout{$c \nateq f$} \\
      $c \natrev g$ &               \\ 
                    & $e \natfor b$ \\
      $e \natfor c$ &               \\[-1ex]
      $\vdots$      & $\vdots$ \\
      \bottomrule
    \end{tabular}
